COSC3500 \\ 2D Orbital Simulation Report

### 2018-10-19 reports/ms1_report.tex
Better data analysis

% The testing actually performed [Do not rewrite your previous section to match this]. Comment on any differences between your test plan and what you actually executed. Give your results.
All valid combinations\footnote{As an example, \texttt{--ntasks-per-node=8, cpus-per-task=8} is not an admissable configuration, as this would require 64 CPUs on a single node. \texttt{dogmatix} only has nodes with 24 or 28 CPUs} of the values in the lists above were performed. Tweaks in the number of bodies ($n$) (a step from 4 to 16 bodies is double the body density; tests with 16384 bodies did not terminate), \texttt{--nodes} (\texttt{dogmatix} only has 12 nodes in the \texttt{cosc} partition; it did not make sense to disable MPI) and not setting \texttt{--ntasks} parameter (it made sense to allow Slurm to dynamically allocate the required number of tasks based on our \texttt{--ntasks-per-node} and \texttt{--cpus-per-task} parameters) and adding the \texttt{--ntasks-per-node} parameter. Further granuality in the \texttt{--cpus-per-task} parameter was also introduced.

@@

We measure time with a combination of the \texttt{sys} and \texttt{user} times reported by the \texttt{time} core util.

We can see a few trends emerge

\begin{itemize}
    \item \texttt{--ntasks-per-node=\{tasks\_per\_node\}} causes time to be an order of magnitude higher, across

\end{itemize}
- Simulations with Barnes-Hut enables have  lrunning times are smaller than their Barnes-Hut disabled counterparts, except on when TODO

>>>>

We test with 10 \texttt{numTimeSteps}, to drown out the time dedicated to input parsing and upfront memory allocation (which is in the vicinity of 100ms).

% The testing actually performed [Do not rewrite your previous section to match this]. Comment on any differences between your test plan and what you actually executed. Give your results.
All valid combinations\footnote{As an example, \texttt{--ntasks-per-node=8, cpus-per-task=8} is not an admissable configuration, as this would require 64 CPUs on a single node. \texttt{dogmatix} only has nodes with 24 or 28 CPUs} of the values in the lists above were performed. Tweaks in the number of bodies ($n$) (a step from 4 to 16 bodies is double the body density; tests with 16384 bodies did not terminate), \texttt{--nodes} (\texttt{dogmatix} only has 12 nodes in the \texttt{cosc} partition; it did not make sense to disable MPI), not setting \texttt{--ntasks} parameter (it made sense to allow Slurm to dynamically allocate the required number of tasks based on our \texttt{--ntasks-per-node} and \texttt{--cpus-per-task} parameters) and adding the \texttt{--ntasks-per-node} parameter were made since our MS2 plan. Further granuality in the \texttt{--cpus-per-task} parameter was also introduced.

@@

We measure time with a combination of the \texttt{sys} and \texttt{user} times reported by the \texttt{time} coreutil.

We can see a few trends emerge:

\texttt{--ntasks-per-node=8} causes time to be above an order of magnitude higher, across all results. This behaviour is most pronounced when testing with 4096 bodies, across a variable number of nodes. We can also see the pronounced effect of Barnes-Hut ($O(n \log n)$) at 4096 bodies.

\includegraphics[width=14.2cm]{4096-nodes-tasksPerNode}

The behaviour becomes less significant when increasing the number of CPUs per task, resulting in maximum CPU utilization per node. I hypothesize that process context switch overhead is causing this behaviour, as having a greater number of tasks allocated to a node than available CPUs causes the CPU (or CPUs) to multiprocess tasks.

\includegraphics[width=14.2cm]{4096-cpusPerTask-tasksPerNode}

Furthermore, the behaviour is still pronounced at 4 bodies, and the resulting times at \texttt{--ntasks-per-node=8} do not appear to be a function of the number of bodies.

\includegraphics[width=14.2cm]{4-cpusPerTask-tasksPerNode}
